---
title: "R homework -- Degree distribution and connected components"
date: "MAT690 NetSci - Ye Chen"
output:
  html_document:
    toc: yes
---


#### Problem 1. 
Generate a random network $G(n,p)$. If there are too many vertices and edges, you can change the edge size and vertex size for a better figure.
```{r}
library(igraph)
n=500 #number of nodes
p=0.003 #probability 
g <- erdos.renyi.game(n, p, type = "gnp") #generate a random graphs in G(n,p) 
plot(g, vertex.label= NA, edge.arrow.size=0.02,vertex.size = 0.5, xlab = "Random Network: G(N,p) model")
```

Check the degree of each vertex.
```{r}
degree(g) 
```

You can summerize the degree distribution using one of the following commands.
```{r}
hist(degree(g))
degree_distribution(g)
plot(0:max(degree(g)),degree_distribution(g)) 
plot(0:max(degree(g)),degree_distribution(g),type = "l", col="green")
```

Next, compare the theoretical distribution to the simulated distributions. The red curve is the theoretical distribution, green curve is the simulated distribution.
```{r, animation.hook="gifski"}
library(gifski)
k=0:20
simulation_number=10
for (i in 1:simulation_number){
  #hold on for the next graph
  g <- erdos.renyi.game(n, p, type = "gnp") #generate a random graphs in G(N,p) 
  plot(k,((n-1)*p)^k*exp(p-n*p)/factorial(k), type = "l", col = "red",xlim = c(0,20),ylim = c(0,1),ylab = NA)
  par(new=TRUE)
  plot( 0:max(degree(g)), degree_distribution(g),type = "l", col="green" ,xlim = c(0,20),ylim = c(0,1))
  #you can skip the par(new=TRUE) command if you replace the second 'plot' by 'lines' as the following
  #lines( k[1:length(degree_distribution(g))], degree_distribution(g), col="green" ,xlim = c(0,50),ylim = c(0,1))
}
dev.off()
```
#### <span style="color: red;"> Your job. </span> 
Pick a large unweighted undirected network you think the connections between any two nodes should be random in http://networkrepository.com/. 

(1) Plot the network.

(2) Plot the degree distribution together with the Poisson distribution. 

(3) Does the network you picked has the degree distribution close to a Poisson distribution?

#### Problem 2. 

We are to simulate some networks using the $G(n,p)$ model and discover how the p related to u (the size of the largest connected component/N).
```{r}
n=500
p=0.0016
g <- erdos.renyi.game(n, p, type = "gnp") #generate a random graphs in G(N,p) 
```
 
```{r}
comp <- components(g)
comp
comp$csize
max(comp$csize)
max(comp$csize)/n #this is u
```
Generate 50 random graphs, and compute the average u.
```{r}
simulation_number=50
simulation_result=rep(0,simulation_number)
for (i in 1:simulation_number){
  g <- erdos.renyi.game(n, p, type = "gnp")
  simulation_result[i]=max(comp$csize)/n
}
mean(simulation_result)
```
#### <span style="color: red;"> Your job. </span> 
Generate 100 different p in a reasonable range, compute the mean of u for different p.

(1) Plot the p-u curve.

(2) Do you see that for large p, the network is always connected? (If not, make the p large enough to see it.)
